Capstone Movielens Report

### 2025-12-14 reports/capstone-movielens.site/05.appendix.Rmd
Functions described:   - `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0`;   - `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1`;   - `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2`.

(Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

::: {.noteblock data-latex=""}
When the value is $NA$ (default), $1$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
:::
:::
::: { #func.loess_de.args.span .sidebar }
###### ***span***
\

(Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

::: {.noteblock data-latex=""}
When the value is $NA$ (default), $0.75$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
:::
:::
:::

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above;

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above.

@@

::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.

@@

::: { #func.train_UMGY_SmoothedDay_effect.cv.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.cv.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.

@@

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above.

@@

The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) function is shown below:
```{r eval=FALSE}
```

@@

>>>>

(Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

::: {.noteblock data-latex=""}
When the value is `NA` (default), $1$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
:::
:::
::: { #func.loess_de.args.span .sidebar }
###### ***span***
\

(Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

::: {.noteblock data-latex=""}
When the value is `NA` (default), $0.75$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
:::
:::
:::

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above;

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above.

@@

::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.

@@

::: { #func.train_UMGY_SmoothedDay_effect.cv.args.degree .sidebar }
  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.cv.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.

@@

```{r eval=FALSE}
  lss.UMGYDE.preset.degree0.result <- 
    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree0)
```

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

@@

The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect.RMSE.cv.degree0 <- function(span) {
  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 0, span)
}
```

@@

#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1}
\

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $0$.

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
lss.UMGYDE.fine_tune.degree1.result <- 
  model.tune.param_range(lss.fine_tune.loop_starter,
                         UMGYDE.fine_tune.degree1.data.path,
                         cache_file.base_name,
                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree1)
```

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
:::
:::

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args .sidebar }
##### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details .sidebar }
##### Details
\

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.value .sidebar }
##### Value
\

The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.code .sidebar }
##### Source Code
\

The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect.RMSE.cv.degree1 <- function(span) {
  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 1, span)
}
```

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) script on _GitHub_.
:::
:::

#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2}
\

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $0$.

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
lss.UMGYDE.fine_tune.degree2.result <- 
  model.tune.param_range(lss.fine_tune.loop_starter,
                         UMGYDE.fine_tune.degree2.data.path,
                         cache_file.base_name,
                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree2)
```

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
:::
:::

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args .sidebar }
##### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details .sidebar }
##### Details
\

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.value .sidebar }
##### Value
\

The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.code .sidebar }
##### Source Code
\

The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect.RMSE.cv.degree2 <- function(span) {
  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 2, span)
}
```

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) script on _GitHub_.
:::
:::
